Test SUSIE for regions near genes (500kb flanking)

### 2020-06-22 analysis/simulation-mr.ash2s-ukbchr22-gtex.adipose.Rmd
fix sa2 bug; locus zoom

## Simulation 1
True parameters:
```{r para 1}
load(paste0(simdatadir, "simu_20200616-1-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200616-1.R"))
```

MR.ASH2s results (start from gene):
```{r sim 1 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200616-1-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-1"
simtag <- "20200616-1"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

MR.ASH results (start from SNP):
Very similar to start from gene, therefore, not shown.
```{r sim 1 snp, eval = F}
load(paste0(outputdir, "20200616-1-mr.ash2s.snp-res.Rd"))
g.fit <- mr.ash2s.fit$fit2
s.fit <-  mr.ash2s.fit$fit1
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-1"
simtag <- "20200616-1"
plot_all(paste0(outputdir, tag, "-mr.ash2s.snp-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.snp-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 2}
load(paste0(simdatadir, "simu_20200616-2-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200616-2.R"))
```

MR.ASH results (start from gene):
```{r sim 2 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200616-2-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-2"
simtag <- "20200616-2"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 3}
load(paste0(simdatadir, "simu_20200616-3-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200616-3.R"))
```

MR.ASH results (start from gene):
```{r sim 3 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200616-3-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-3"
simtag <- "20200616-3"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 4}
load(paste0(simdatadir, "simu_20200616-4-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200616-4.R"))
```

MR.ASH results (start from gene):
```{r sim 4 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200616-4-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-4"
simtag <- "20200616-4"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

>>>>

## Simulation 1
MR.ASH2s results (start from gene):
```{r sim 1 gene, out.width = "98%", out.height="95%"}
tag <- "20200616-1"
tag2 <- "expr-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```

MR.ASH results (start from SNP):
```{r sim 1 snp, eval = F}
tag <- "20200616-1"
tag2 <- "snp-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```

@@

MR.ASH results (start from gene):
```{r sim 2 gene, out.width = "98%", out.height="95%"}
tag <- "20200616-2"
tag2 <- "expr-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```
MR.ASH results (start from snp):
```{r sim 2 snp, out.width = "98%", out.height="95%"}
tag <- "20200616-2"
tag2 <- "snp-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```

@@

MR.ASH results (start from gene):
```{r sim 3 gene, out.width = "98%", out.height="95%"}
tag <- "20200616-3"
tag2 <- "expr-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```
MR.ASH results (start from snp):
```{r sim 3 snp, out.width = "98%", out.height="95%"}
tag <- "20200616-3"
tag2 <- "snp-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```

@@

MR.ASH results (start from gene):
```{r sim 4 gene, out.width = "98%", out.height="95%"}
tag <- "20200616-4"
tag2 <- "expr-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```

MR.ASH results (start from snp):
```{r sim 4 snp, out.width = "98%", out.height="95%"}
tag <- "20200616-4"
tag2 <- "snp-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```

## Simulation 5

MR.ASH results (start from gene):
```{r sim 5 gene, out.width = "98%", out.height="95%"}
tag <- "20200616-5"
tag2 <- "expr-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)

plot_all(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt"), paste0(outputdir, tag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt"), paste0(outputdir, tag, ".snpgwas.txt.gz"))
```

MR.ASH results (start from SNP):
```{r sim 5 snp, out.width = "98%", out.height="95%"}
tag <- "20200616-5"
tag2 <- "snp-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)

plot_all(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt"), paste0(outputdir, tag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt"), paste0(outputdir, tag, ".snpgwas.txt.gz"))
```

## Simulation 6

MR.ASH results (start from gene):
```{r sim 6 gene, out.width = "98%", out.height="95%"}
tag <- "20200616-6"
tag2 <- "expr-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)

plot_all(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt"), paste0(outputdir, tag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt"), paste0(outputdir, tag, ".snpgwas.txt.gz"))
```

MR.ASH results (start from SNP):
```{r sim 6 snp, out.width = "98%", out.height="95%"}
tag <- "20200616-6"
tag2 <- "snp-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)

plot_all(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt"), paste0(outputdir, tag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt"), paste0(outputdir, tag, ".snpgwas.txt.gz"))
```

### 2020-06-22 analysis/simulation-simpleveb-boost2-ukbchr22.Rmd
fix sa2 bug; locus zoom

>>>>

## Simulation 5

MR.ASH results (start from gene):
```{r sim 5 gene, out.width = "98%", out.height="95%"}
tag <- "20200527-5"
tag2 <- "expr-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)

plot_all(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt"), paste0(outputdir, tag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt"), paste0(outputdir, tag, ".snpgwas.txt.gz"))
```

MR.ASH results (start from SNP):
```{r sim 5 snp, out.width = "98%", out.height="95%"}
tag <- "20200527-5"
tag2 <- "snp-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```

## Simulation 6

MR.ASH results (start from gene):
```{r sim 6 gene, out.width = "98%", out.height="95%"}
tag <- "20200527-6"
tag2 <- "expr-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)

plot_all(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt"), paste0(outputdir, tag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt"), paste0(outputdir, tag, ".snpgwas.txt.gz"))
```

MR.ASH results (start from SNP):
```{r sim 6 snp, out.width = "98%", out.height="95%"}
tag <- "20200527-6"
tag2 <- "snp-res"

param <- read.table(paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt"), header = T, row.names = 1)
print(param)
```

### 2020-06-22 analysis/simulation-susie-ukbchr22.Rmd
fix sa2 bug; locus zoom

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=F)
```

@@

Zoomlocus view for CBX7 region:
```{r zoomlocus, out.width = "85%", eval = T}
file.copy("/home/simingz/causalTWAS/simulations/simulation_ashtest_20200503/snp_200622_CBX7/chr22_39026778-40048655.pdf", "output")
knitr::include_graphics("output/chr22_39026778-40048655.pdf")
```
